---
title: "Statnew"
author: "NatashaKarwal"
date: "8/1/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(readr)
library(ggplot2)
library(dplyr)
library(reshape2)
library(leaps)
library(lmtest)
library(car)
```

```{r}
nb12<- read.csv("/Users/nk106/OneDrive/Documents/apple.csv", header=TRUE)
nb12
summary(nb12)
```

#Full Model
#Even though R^2 and adjusted R^2 are high, this may not necessarily confirm
#the model being a favourable one. Also, R^2 and adjusted R^2 are good 
#comparisons for models with same number of parameters. 
```{r}
Fullmodelp<- lm(vixchange ~.-day, data=nb12)
summary(Fullmodelp)
```
#Main focus is to predict vixchange based on covid indicators but the subset
#choice below of variables differs from our main focus since it has chosen
#stock related variables. 
```{r}
testsub<-regsubsets(vixchange ~.-day, data=nb12)
bestsubt<-summary(testsub)
bestsubt
```

```{r}
newfull<- nb12%>%
  select(vixchange,vixprevious,vixchangepercent,confirmedtotal,confirmedprevious,confirmedchangepercent,deathstotal,deathsprevious,deathschangepercent)
newfull
```
#Partial Regression Plots without stock related variable 
```{r}
regplot<-lm(vixchange ~., data=newfull)
summary(regplot)
```

#Added-variable plot (partial regression plot)
#Reference line appears almost flat for most 
#does not seem to be highly correlated with the response variable
```{r}
avPlots(regplot)
```

#DW=2.254 seems favourable
```{r}
dwtest(regplot)
```
#Variance Inflation Factor (VIF)
#There seems moderate correlation between predictors for vix and volume. 
#Others are highly correlated 
```{r}
vif(Fullmodelp)
```




